### 2017-03-29 main.tex
Update response2 document. Re-hyphenate compound adjective ;)
Respond to last comments from the editor: moved ylabel on Fig3, and changed one word.

A variety of syllable-triggering systems have been used, but few have
been documented or characterised in detail.  In 1999,
detection was achieved by a group of IIR filters with hand-tuned logical
operators \cite{Leonardo1999}.  The system had a latency of 50 or 100 ms,
and accuracy and jitter were not reported.  As access to
computational resources has improved, approaches have changed: in
2009, hand-tuned filters were implemented on a Tucker-Davis Technologies digital signal processor, bringing latency down to around 4 ms \cite{Andalman2009}. But as with other filter-bank techniques, it
is not strictly a syllable detector but rather a pitch and timbre
detector---it cannot identify a frequency sweep, or distinguish a
short chirp from a long one---and thus requires careful selection of
target syllables.  Furthermore, the method is neither inexpensive nor,
based on our experience with a similar technique, accurate.
2009 saw the application of a neural network to a spectral image of
song \cite{Keller2009}.  They reported a jitter of 4.3 ms, but further implementation and
performance details are not available.  In 2011, stable portions of syllables were matched to spectral templates in 8 ms
segments \cite{Warren2011}.  This detector achieved a jitter of 4.5 ms, and false-negative and
false-positive rates of up to 2\% and 4\% respectively.  Hardware
requirements and ease of use were not reported.  In 2013, spectral
images of template syllables were compared to song using a correlation coefficient \cite{Skocik2013}.  With a
fast desktop (Intel i7 six-core) running Linux and equipped with a
National Instruments data acquisition card, it boasts a hardware-only
(not accounting for the time taken to compute a match with a syllable)
latency and jitter of just a few microseconds, and the detection
computation they use should not much increase that.  They reported
false-negative rates around 4\% and 7\% for zebra finches and
Bengalese finches respectively, measured on a small dataset.  In much
other work, a syllable detector is alluded to, but not described.

@@

\subsection{Learning a detector}

@@

\begin{figure}
  % Width 8, height 3, font 120%
  \includegraphics[width=\textwidth]{Fig3}
  %\includegraphics[width=\textwidth]{accuracies-2hidden}

@@

\bibliography{birds}

>>>>

A variety of syllable-triggering systems have been used, but few have
been documented or characterised in detail.  In 1999,
detection was achieved by a group of IIR filters with hand-tuned logical
operators \cite{Leonardo1999}.  The system had a latency of 50 or 100 ms,
and accuracy and jitter were not reported.  As access to
computational resources has improved, approaches have changed: in
2009, hand-tuned filters were implemented on a Tucker-Davis Technologies digital signal processor, bringing latency down to around 4 ms \cite{Andalman2009}. But as with other filter-bank techniques, it
is not strictly a syllable detector but rather a pitch and timbre
detector---it cannot identify a frequency sweep, or distinguish a
short chirp from a long one---and thus requires careful selection of
target syllables.  Furthermore, the method is neither inexpensive nor,
based on our experience with a similar technique, accurate.
2009 saw the application of a neural network to a spectral image of
song \cite{Keller2009}.  They reported a jitter of 4.3 ms, but further implementation and
performance details are not available.  In 2011, stable portions of syllables were matched to spectral templates in 8-ms
segments \cite{Warren2011}.  This detector achieved a jitter of 4.5 ms, and false-negative and
false-positive rates of up to 2\% and 4\% respectively.  Hardware
requirements and ease of use were not reported.  In 2013, spectral
images of template syllables were compared to song using a correlation coefficient \cite{Skocik2013}.  With a
fast desktop (Intel i7 six-core) running Linux and equipped with a
National Instruments data acquisition card, it boasts a hardware-only
(not accounting for the time taken to compute a match with a syllable)
latency and jitter of just a few microseconds, and the detection
computation they use should not much increase that.  They reported
false-negative rates around 4\% and 7\% for zebra finches and
Bengalese finches respectively, measured on a small dataset.  In much
other work, a syllable detector is alluded to, but not described.

@@

\subsection{Training a detector}

@@

\begin{figure}
  % Width 10, height 4, font 100%
  \includegraphics[width=\textwidth]{Fig3}
  %\includegraphics[width=\textwidth]{accuracies-2hidden}

@@

%\bibliography{birds}
\begin{thebibliography}{10}

\bibitem{Kao2005}
Kao MH, Doupe AJ, Brainard MS.
\newblock Contributions of an avian basal ganglia--forebrain circuit to
  real-time modulation of song.
\newblock Letters to Nature. 2005 February;433:638--643.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v433/n7026/abs/nature03127.html}.

\bibitem{Wang2008interhemispheric}
Wang CZH, Herbst JA, Keller GB, Hahnloser RHR.
\newblock Rapid Interhemispheric Switching during Vocal Production in a
  Songbird.
\newblock PLOS Biology. 2008 October;6(10).
\newblock Available from:
  \url{http://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.0060250}.

\bibitem{Keller2009}
Keller GB, Hahnloser RHR.
\newblock Neural processing of auditory feedback during vocal practice in a
  songbird.
\newblock Nature. 2009 January;457:187--190.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v457/n7226/abs/nature07467.html}.

\bibitem{Tumer2007pitchshift}
Tumer EC, Brainard MS.
\newblock Performance variability enables adaptive plasticity of 'crystallized'
  adult birdsong.
\newblock Nature. 2007 December;450:1240--1244.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v450/n7173/abs/nature06390.html}.

\bibitem{Andalman2009}
Andalman AS, Fee MS.
\newblock A basal ganglia-forebrain circuit in the songbird biases motor output
  to avoid vocal errors.
\newblock Proceedings of the National Academy of Sciences of the United States
  of America. 2009 July;106(30):12518--12523.
\newblock Available from:
  \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC2709669/}.

\bibitem{Charlesworth2011learning}
Charlesworth JD, Tumer EC, Warren TL, Brainard MS.
\newblock Learning the microstructure of successful behavior.
\newblock Nature Neuroscience. 2011;14(3):373--380.
\newblock Available from:
  \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3045469/}.

\bibitem{Warren2011}
Warren TL, Tumer EC, Charlesworth JD, Brainard MS.
\newblock Mechanisms and time course of vocal learning and consolidation in the
  adult songbird.
\newblock Journal of Neurophysiology. 2011 October;106(4):1806--1821.
\newblock Available from:
  \url{http://jn.physiology.org/content/106/4/1806.full}.

\bibitem{Canopoli2014}
Canopoli A, Herbst JA, Hahnloser RHR.
\newblock A Higher Sensory Brain Region Is Involved in Reversing
  Reinforcement-Induced Vocal Changes in a Songbird.
\newblock The Journal of Neuroscience. 2014;34(20):7018--7026.
\newblock Available from:
  \url{http://www.jneurosci.org/content/34/20/7018.full}.

\bibitem{Leonardo1999}
Leonardo A, Konishi M.
\newblock Decrystallization of adult birdsong by perturbation of auditory
  feedback.
\newblock Nature. 1999 June;399:466--470.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v399/n6735/abs/399466a0.html}.

\bibitem{Skocik2013}
Skocik M, Kozhevnikov A.
\newblock Real-time system for studies of the effects of acoustic feedback on
  animal vocalizations.
\newblock Frontiers in Neural Circuits. 2013 January;6(111).
\newblock Available from:
  \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3539774/}.

\bibitem{Poole2012}
Poole B, Markowitz JE, Gardner TJ.
\newblock The Song Must Go On: Resilience of the Songbird Vocal Motor Pathway.
\newblock PLOS One. 2012 June;7(6).
\newblock Available from:
  \url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0038173}.

\bibitem{Tchernichovski2011SAP}
Tchernichovski O. Sound Analysis Pro User Manual; 2011.
\newblock Available from: \url{http://soundanalysispro.com/manual-1}.

\bibitem{Jacobsen2003SlidingDFT}
Jacobsen E, Lyons R.
\newblock The sliding DFT.
\newblock IEEE Signal Processing Magazine. 2003 Mar;20(2):74--80.
\newblock Available from:
  \url{http://www.cmlab.csie.ntu.edu.tw/DSPCourse/reference/Sliding\%20DFT.pdf}.

\bibitem{hkp}
Hertz JA, Krogh AS, Palmer RG.
\newblock Introduction to the Theory of Neural Computation.
\newblock Perseus Books; 1991.

\bibitem{Noll1970pitchdetection}
Noll AM.
\newblock Pitch determination of human speech by the harmonic product spectrum,
  the harmonic sum spectrum, and a maximum likelihood estimate.
\newblock In: Proceedings of the symposium on computer processing in
  communications. vol.~19; 1970. p. 779--797.

\end{thebibliography}
